\documentclass[12pt]{llncs}

\usepackage{rex}

\usepackage{stmaryrd}
\usepackage[retainorgcmds]{IEEEtrantools}

% alternative caligraphy
\usepackage{calrsfs}
\DeclareMathAlphabet{\pazocal}{OMS}{zplm}{m}{n}

% alternative caligraphy
\DeclareFontFamily{U}{mathc}{}
\DeclareFontShape{U}{mathc}{m}{it}%
{<->s*[1.03] mathc10}{}
\DeclareMathAlphabet{\mathscr}{U}{mathc}{m}{it}

% minted python shortcut
\newminted{py}{frame=single,breaklines,autogobble,fontfamily=zi4,
escapeinside=||,mathescape=true,style=bw,linenos,python3=true}

\spnewtheorem{thing}{Thing}{\bfseries}{\itshape}

\newdate{date}{8}{10}{2019}

\begin{document}
\displaydate{date}

``Synthesize program safety spec by learning from membership''?

Let $X = \{x_1, ..., x_i\}$ be the named program variables.
Let $N = \{n_1, ..., n_i\}$ be the numeric variables
of finite domain.
Let atomic predicates involving $x_i,x_j,n_i$ be of
the form $x_i <= x_j\ |\ x_i <= n_i\ |\ n_i <= x_i$.
Let $B$ representing a set of safety-violating program states
be a formula of atomic predicates involving $X,N$.
The safety problem is to check $SAT(B)$.

Let $B$ be not explicitly known. Suppose an honest oracle $O$
that answers membership query is given; this can be a human
teacher who knows if some certain state $B(X_k,N_k)$ realized
by concrete valuations of $X_k,N_k$ is undesirable but
at the same time cannot give a full account of $B$. (Impossible?)

The goal is to check $SAT(B)$ by learning the specification of
$B$ from $O$.

\begin{thing}
Can we know if $SAT(B)$ \emph{can} be answered efficiently?
(Property Testing)

If so, can we learn $B$ efficiently in such a way that allows
$SAT(B)$ be checked efficiently?
(Learnability)

For example, can we test if $B$ \emph{can}
be represented in horn, and, if so, what is it in horn?

If not, can we answer $SAT(B)$ without knowing $B$? Perhaps
by synthesizing a ``good enough'' hypothesis $H$ such that
$SAT(H)$ can be answered efficiently and that
(Approximation) $\|B - H\| <= \epsilon$ or
(Overapproximation) $H \to B$?
\end{thing}

\begin{thing}[Property Testing]
What are the characterizing properties of the concept
class $E$ such that $SAT(e)$ can be checked efficiently
for all $e \in E$? Can these properties be checked efficiently?

If such $E$ cannot exist, what are the ``useful'' classes
$E_1, .. E_n$ that can cover ``most'' practical cases?

For example, what are the properties of the class of horns $H$,
maybe in terms of their Fourier spectrum? And how to check if
$B \in H$ efficiently?
\end{thing}

\begin{thing}[Learnability]
If we know there is an representation of $B$ with which
$SAT(B)$ \emph{can} be answered efficiently, how to learn that
representation efficiently?

%if there's no such representation, what's a ``nice''
%representation of it that is ``good'' for SAT solvers?
\end{thing}

%membership only, because humans can only answer memberships

\end{document}
